Towards typed repositories of proofs

### 2010-06-18 papers/MIPS2010/abstract.tex
...
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@114 403e655e-980a-47bd-8c60-1ee5348bb6b7

Representing syntax and logics is nicely done in a \emph{logical
  framework} like LF (\cite{harper1993framework}): both the syntactic
elements and the typing derivations can sit in the same tree
structure, and both can be rechecked at the same time, thanks to
dependent types. For the purpose of incremental type checking though,
our needs are a little bit different: first, we need to record, that
is to name all intermediate values of our developments, so as to be
able to address and reuse them multiple times. Secondly, we need to
make sure that those intermediate values (sub-terms) are not recorded
twice, so as to not type-check them twice: we are looking to represent
syntactic and typing objects as a DAG rather than a tree.

>>>>

Representing syntax and logics is nicely done in a \emph{logical
  framework} like LF: both the syntactic
elements and the typing derivations can sit in the same tree
structure, and both can be rechecked at the same time, thanks to
dependent types. For the purpose of incremental type checking though,
our needs are a little bit different: first, we need to record, that
is to name all intermediate values of our developments, so as to be
able to address and reuse them multiple times. Secondly, we need to
make sure that those intermediate values (sub-terms) are not recorded
twice, so as to not type-check them twice: we are looking to represent
syntactic and typing objects as a DAG rather than a tree.
